Pre-/Post-Trikafta in CFRD

### 2022-04-28 Colleen Wood/Pre-post Trikafta/pre_post_trikafta_analysis.Rmd
fixed stupid DOB issue

@@

@@

df$Age = pmax(as.numeric(difftime(df$Date,df$DOB,units = "days")),df$Age,na.rm = T)/365.25

@@

df = df %>% arrange(Site,CFF.ID,Date)

@@

# Most recent before/after - limit to 2 years before start
# Want the value closest to start date before start, and most recent with respect to now from start
# (i.e. the longest time after start)
most_recent = df %>% group_by(CFF.ID,Site,Before_After) %>%
  mutate(time_new = max(Time) - Time) %>%
  arrange(time_new) %>% 
  summarise(BMIz = first(na.omit(BMIz)),ppFEV = first(na.omit(ppFEV)),
            ppFVC = first(na.omit(ppFVC))) %>%
  arrange(Site,CFF.ID,Before_After)
t = df %>% select(CFF.ID,Site,Date,Time,Before_After,BMIz,ppFEV,ppFVC) %>%
  group_by(CFF.ID,Site,Before_After) %>%
  arrange(Site,CFF.ID,Before_After)
keep = most_recent %>% group_by(CFF.ID) %>% count() %>% filter(n == 2)

@@

>>>>

# Fix incorrect century (WHY LUBRIDATE WHY?!)
df$DOB[which(df$DOB > lubridate::mdy("1/1/2022"))] = 
  df$DOB[which(df$DOB > lubridate::mdy("1/1/2022"))] - years(100)

@@

um$Age = um$Age / 365.25

@@

df$Age = pmax(as.numeric(difftime(df$Date,df$DOB,units = "days"))/365.25,df$Age,na.rm = T)

@@

df = df %>% arrange(Site,CFF.ID,Date) %>% distinct()

@@

@@

```{r}
# Most recent before/after - limit to 2 years before start
# Want the value closest to start date before start, and most recent with respect to now from start
# (i.e. the longest time after start)
most_recent = df %>% group_by(CFF.ID,Site,Before_After) %>%
  mutate(time_new = max(Time) - Time) %>%
  arrange(time_new) %>% 
  summarise(BMIz = first(na.omit(BMIz)),ppFEV = first(na.omit(ppFEV)),
            ppFVC = first(na.omit(ppFVC))) %>%
  arrange(Site,CFF.ID,Before_After)
t = df %>% select(CFF.ID,Site,Date,Time,Before_After,BMIz,ppFEV,ppFVC) %>%
  group_by(CFF.ID,Site,Before_After) %>%
  arrange(Site,CFF.ID,Before_After)
keep = most_recent %>% group_by(CFF.ID) %>% count() %>% filter(n == 2)
```
